A Large-scale Study of Polymorphism in R

### 2019-04-02 paper/main.tex
small todoo list for data tmr
minor

Thus L0 includes the following types: vectors of primitive types (integers
\I, double \D, character \C, logical \L, raw \R, complex \X), lists of any
type (\l), and scalar values (environment \sE, closures \sF, symbols \sS and
null \sN). We add the type \ANY to stand in for any type.

@@

\section{Results}\label{sec:results}

Having built an understanding of our data collection and analysis pipeline,
we will turn our attention to the results of our analysis.

\subsection{L0}

In this section, we will begin by breaking down our corpus of data with L0
in mind.  From this perspective, we will see how current R programmers see
types in the language, and we will leverage our newfound insight to design a
type system which should be relevant to them.

Without further ado, let's look at the data, first focusing on a broad
overview of the polymorphism in L0.  Figure~\ref{fig:L1argcounts} shows the
polymorphicity of argument positions in R function.  From there, we build up
a picture of the polymorphicity of functions as a whole, and the data for
this function polymorphism can be found in Figure~\ref{fig:L1funcounts}.

% latex table generated in R 3.5.1 by xtable 1.8-3 package
% Fri Mar 29 18:10:23 2019
\begin{table}[ht]
\label{fig:L1argcounts}
\centering
\begin{tabular}{lrr}
  \hline
Type & Count & Percentage \\
  \hline
Full Monomorphic & 784K & 85.76 \\
  Monomorphic in Type & 845K & 92.46 \\
  Monomorphic in Class & 827K & 90.41 \\
  Monomorphic in Attribute Pattern & 825K & 90.27 \\
  Total Seen & 914K & --- \\
   \hline
\end{tabular}
\caption{typeof type system (L0) (arguments)}
\end{table}
% latex table generated in R 3.5.1 by xtable 1.8-3 package
% Fri Mar 29 18:10:23 2019
\begin{table}[ht]
\label{fig:L1funcounts}
\centering
\begin{tabular}{lrr}
  \hline
Type & Count & Percentage \\
  \hline
Full Monomorphic & 144K & 66.54 \\
  Monomorphic in Type & 173K & 80.16 \\
  Monomorphic in Class & 163K & 75.21 \\
  Monomorphic in Attribute Pattern & 161K & 74.37 \\
  Total Seen & 216K & --- \\
   \hline
\end{tabular}
\caption{typeof type system (L0) (functions)}
\end{table}

@@

@@

>>>>

Thus L0 includes the following types: vectors of primitive types (integers
\I, double \D, character \C, logical \L, raw \R, complex \X), lists of any
type (\l), and scalar values (environment \sE, closures \sF, symbols \sY, S4
object \sS, and null \sN). We add the type \ANY to stand in for any type.

@@

\section{Analysis Results}\label{sec:results}

This section presents our results for each of the levels we have considered.

\subsection{L0 polymorphism}

At L0, the type system is aligned with the types of the core language.  We
have observed over 173K monomorphic functions; this accounts for 80\% of our
corpus.  In terms of argument positions, 92\% of arguments are monomorphic.

Figure~\ref{fig:L1argcounts} shows the polymorphicity of argument positions
 in R function.  From there, we build up a picture of the polymorphicity of
 functions as a whole, and the data for this function polymorphism can be
 found in Figure~\ref{fig:L1funcounts}.

% latex table generated in R 3.5.1 by xtable 1.8-3 package
% Fri Mar 29 18:10:23 2019
\begin{table}[ht]\label{fig:L1argcounts}\centering\begin{tabular}{lrr}  \hline
Type                   & Count & Percentage \\  \hline
Full Monomorphic       & 784K & 85.76 \\
  Monomorphic in Type & 845K & 92.46 \\
  Monomorphic in Class & 827K & 90.41 \\
  Monomorphic in Attribute Pattern & 825K & 90.27 \\
  Total Seen & 914K & --- \\
   \hline
\end{tabular}
\caption{typeof type system (L0) (arguments)}
\end{table}
% latex table generated in R 3.5.1 by xtable 1.8-3 package
% Fri Mar 29 18:10:23 2019
\begin{table}[ht]
\label{fig:L1funcounts}
\centering
\begin{tabular}{lrr}
  \hline
Type & Count & Percentage \\
  \hline
Full Monomorphic & 144K & 66.54 \\
  Monomorphic in Type & 173K & 80.16 \\
  Monomorphic in Class & 163K & 75.21 \\
  Monomorphic in Attribute Pattern & 161K & 74.37 \\
  Total Seen & 216K & --- \\
   \hline
\end{tabular}
\caption{typeof type system (L0) (functions)}
\end{table}

@@

\AT{TODO number of colocated primitive/other classes. Could use to suggest some optional class annotation.
Maybe grab full class poly to see if there's something big? Without collapse to primitives.}

@@

\AT{TODO control for the common cases?}
